Add Data

### 2025-02-12 data.qmd
Don't remove .row_id
This was only necessary because we
previously used tinytable to export
the data dictionary. Now that we use
datawizard, we can leave them in,
making the code easier to read and
understand.
Provide examples more examples

datawizard::data_codebook(dat) |>
  datawizard::data_select(exclude = c("ID", ".row_id")) |>
  datawizard::data_filter(N != "") |>
  datawizard::print_md()
```

@@

Depending on the type of data, it may also be necessary
to describe measurement instruments, sampling procedures, appropriate weighting,
applied preprocessing steps, or contact information.
In our case, as the data have already been published,
we only store a reference to its source.

>>>>

datawizard::data_codebook(dat) |>
  datawizard::data_select(exclude = ID) |>
  datawizard::data_filter(N != "") |>
  datawizard::print_md()
```

@@

Depending on the type of data, it may also be necessary
to describe sampling procedures (e.g., selection criteria),
measurement instruments (e.g., questionnaires),
appropriate weighting,
already applied preprocessing steps, or contact information.
In our case, as the data has already been published,
we only store a reference to its source.
